---
title: "P8105 HW5 jam2530"
author: "Jenna Mohammed"
date: '2023-11-12'
output: github_document
---


```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(rvest)
library(purrr)
library(dplyr)
library(ggplot2)
```

# Problem 2 


For this problem, I will examine data from a longtitudal study. I will create and tidy the dataframe, and create a spaghetti plot to display the data

## Data Analysis 

```{r}
# Creating a tidy dataframe listing all files using list.files

file_names <- list.files(path="./hw5_data./data", pattern="\\.csv$", all.files=FALSE, full.names=TRUE)

```

```{r}

# creating a function to read files

all_data <- map_df(file_names, ~ {read.csv(.x)

})

```
 
```{r}
# cleaning and tidying data 

cleaned_df <- all_data |>
  janitor::clean_names() |>
  mutate(subject_ID = as.integer(str_extract(file_names, "[0-9][0-9]"))) |>
  mutate(arm = ifelse(str_detect(file_names, "con") == TRUE, "Control", "Experiment")) 
   
```

### Making a Spaghetti Plot 

```{r}
cleaned_df_new = 
 cleaned_df|>
  pivot_longer(week_1:week_8,
               names_to = "week",
               values_to = "outcome",
               names_prefix = "week_"
               ) |>
  mutate(week = as.numeric(week))

spaghetti_plot <- cleaned_df_new |>
  ggplot(aes(x = week, y = outcome, 
             group = subject_ID, color = arm)) +
  geom_path() +
  labs( x = "Week", 
        y = "Observations",
        title = "Observations vs Time") +
  facet_grid(~arm)
  
spaghetti_plot
```

### Interpertation

The `spaghetti_plot` above depicts the observations of each participant in the longtitudal study over the course of 8 weeks. Both plots have a varying measurements. However, the control graph has observations ranging between -2.5 and 4, while the experiment graph has measurements ranging between -1 and 7.5. Thr experiment graph shows a positive upwards trend.

# Problem 3 

For this problem, I will create a simulation to explore power in a one sample t test. 5000 datasets will be generated  
 

```{r}
# Setting design elements

set.seed(12345)

n <- 30

sigma <- 5

mu <- 0:6

alpha <- 0.05

dataset_total <- 5000

iteration = 1:5000

```

## Data Analysis 

Creating function for hypothesis testing 

```{r}

set.seed(12345)

sigma <- 5

dataset_total <- 5000

iteration = 1:5000

t_test_sim = function(n=30, mu=2, sigma=5) {

  test = tibble(

    x=rnorm(n = n, mean = mu, sd = sigma))

  t_test_results = t.test(x ~ 1, data =test)

  t_test_results|>

    broom::tidy()

}

sim_results =

   tibble(mu = 0:6) |>

   mutate(

    estimate_df = map(.x = mu, ~rerun(dataset_total, t_test_sim(n=30, mu = .x))),

    estimate_dfs = map(estimate_df, bind_rows))|>

    select(-estimate_df)

sim_results

```


```{r}

sim_results =

sim_results %>%

unnest(estimate_dfs) %>%

select(mu, estimate, p.value) %>% mutate(significant = as.numeric(p.value < 0.05))

```


## Plot of Test of Power 

```{r}

power_df <- sim_results |>
  group_by(mu) |>
  mutate(reject_null = p.value < 0.05) |>
  summarize(power_var = mean(reject_null)) 

power_plot <- power_df |> 
  ggplot(aes( x = mu, y = power_var )) +
  geom_path() +
  labs( 
    x = "Mu (True Mean)",
    y = "Power",
    title = "Power of Test versus True Mean Values")

power_plot
```

### Interpertation

A larger power implies a larger effect size. There appears to be a direct positive relationship between the true mean and power, eaning there is a strong probability of correctly rejecting the null


## Plot of Average Estimates 

```{r}

estimate_plot_df <- sim_results |>
  group_by(mu) |>
  mutate(reject_null = p.value < 0.05) |>
  mutate(avg_estimate = mean(estimate)) |>
  mutate(avg_est_reject = mean(estimate[reject_null]))

estimate_plot <- estimate_plot_df |>
  ggplot(aes( x = mu)) +
  geom_line(aes(y = avg_estimate, color = "Average Estimate")) +
  geom_point(aes(y = avg_estimate, color = "Average Estimate")) +
  geom_line(aes(y = avg_est_reject, color = "Average Estimate Alpha < 0.05")) +
  geom_point(aes(y = avg_est_reject, color = "Average Estimate Alpha < 0.05")) +
  labs( x = "True Mean Values",
        y = "Average Estimate of Mu Hat",
        title = "Average Estimate of the True Mean")

estimate_plot
```

### Interpertation

The sample average of mu hat `reject_null` is relatively similar to the true value of mu. The average where the null is rejected is slightly different from the true mean at the start of the graph but aligns towards the end.